The \vspec{} Collection: A suite of utilities to model spectroscopic phase curves of 3D exoplanet atmospheres in the presence of stellar variability.

### 2024-08-14 src/tex/ms.tex
Add missing citations

% Define document class
\documentclass[twocolumn,linenumbers]{aastex631}
\usepackage{showyourwork}
\usepackage[version=4]{mhchem}
\usepackage{listings}
\usepackage{hyperref}

@@

A powerful feature of \texttt{libpypsg} is that it provides a universal interface for 3D atmosphere models and PSG's Global Emission Spectra (GlobES) application \TJ{(Fauchez et al., 2024, in review; see also Kofman et al., 2024, accepted)}.
GlobES expects 3D data to be presented in a binary data format, and converting a model to this format is non-trivial. \texttt{libpypsg}'s \texttt{PyGCM} class provides a native Python representation of GlobES input, and includes built-in methods for converting popular climate models like ExoCAM \citep{wolf2022}, the Whole Atmosphere Community Climate Model \citep[WACCM,][]{marsh2013}, and ExoPlaSim \citep{paradise2022} to the correct format.

@@

T.J. acknowledges support from the Exoplanet Modeling and Analysis Center \citep[EMAC, ][]{renaud2023}.

>>>>

% Define document class
\documentclass[twocolumn,linenumbers]{aastex631}
\usepackage{showyourwork}
\usepackage[version=4]{mhchem}
\usepackage{listings}
\usepackage{hyperref}
\usepackage{natbib}

@@

A powerful feature of \texttt{libpypsg} is that it provides a universal interface for 3D atmosphere models and PSG's Global Emission Spectra (GlobES) application (\citealt{fauchez2024}, in prep; see also \citealt{kofman2024}, accepted)
GlobES expects 3D data to be presented in a binary data format, and converting a model to this format is non-trivial. \texttt{libpypsg}'s \texttt{PyGCM} class provides a native Python representation of GlobES input, and includes built-in methods for converting popular climate models like ExoCAM \citep{wolf2022}, the Whole Atmosphere Community Climate Model \citep[WACCM,][]{marsh2013}, and ExoPlaSim \citep{paradise2022} to the correct format.

@@

T.J. acknowledges support from the Exoplanet Modeling and Analysis Center \citep[EMAC, ][]{renaud2022}.
